---
title: "Interaction_Motifs_Mut_deers"
author: "Miguel Jacome"
date: "18/1/2018"
output: html_document
---

Charging libraries
```{r Used libraries}
library(magrittr)
library(dplyr)
library(reshape2)
library(tidyr)
library(ggplot2)
```


Charging matrix of effectiveness of two populations (visit/day*fruits/day)
```{r Matrix of effectiveness}
matrix_effects_resized <- read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Interaction Motifs/Ant_Mutual_deer/mart_matas_eff.csv")

#Wthout "plant" and "unknown" column
matrix_effects_resized<-matrix_effects_resized[,-1]
matrix_effects_resized<-matrix_effects_resized[,-7]
```


Settings. We obtained the values of seedlings recruiment from the article of Fedriani and Delibes (2011). In this article they measured the recrutiment with: 1) ingested seeds of badger's leaved in open areas and beneath plants (similar to those that surrond our studied plants) and 2) defleshed seeds in open areas and beneath mother plants. We used this information to obtain the dispersal quality of the mutualists frugivorous. We used the recruitment values in open areas of the baddger as a proxy of the foxes (we assumed same seed handling behaviour). Instead for rabbits and rodents we used the recrutiment values of defleshed seeds beneath the mother plant (when these species feed itself, thay defleshed entirely the seeds and leaved ebeneath the mother plant). The wildboars and deers were excluded because they are seed predators.
```{r Seedlings recrutiment values}
rabbit_weight=0.286
rat_weight=0.286
fox_weight=0.179
badger_weight=0.179

```


To define the strengh of interaction for the interaction motifs we obtained the median of "true interactions". Matrix resized (efficiency*recrutiment) by average weights, and adding NA to obtain the median of non-zero interaction values
```{r Median and dispersal quality, include=FALSE}
matrix_effects_resized <-mutate(matrix_effects_resized,
    #Resize effects
    rabbit = rabbit * rabbit_weight,
    rat = rat * rat_weight,
    fox = fox * fox_weight,
    badger = badger * badger_weight)

matrix_effects_resized_NA <- matrix_effects_resized
matrix_effects_resized_NA[matrix_effects_resized_NA==0]<-NA
median <- median(as.matrix(matrix_effects_resized_NA), na.rm=TRUE)
n_row <- nrow(matrix_effects_resized)

my_matrix<-matrix_effects_resized
```


We created a function for the iteration results given the median. Every value beneath the median will be considered as weak, values ≥ median as strong and 0 values as no interaction. The results are a column with the triads of mutualistic and antagonistic interactions based on the interaction strength median and the frequency of the interaction motifs. The antagonistic interactions are composed by wildboar and deer; and mutualistic by rabbit, rat, badger and fox (and a fraction of the deers). Because we have a poor pool of plants, we redesigned  the 9 motifs to 4.*Notice, that a small % of the seeds ingested by deers could escaped the predation process via spitting Castañeda et al. 2017). We divide the interaction of the deers in two: antagonistic deers (deer_a) and mutualistic deers (deer_m). The values of the mutualistic deer represent
```{r Function to obtain Interaction Motifs}

compute_per_category_count <- function(my_matrix, iteration, median, n_row) {
  counts <- mutate( my_matrix,
    #Compute ant and mut effects
    ant = deer_a + wildb,
    mut = (rabbit + rat ) + 
          (fox    + badger),
    class_ant = if_else( ant == 0, "absent", if_else( ant < median, "weak", if_else( ant >= median, "strong", "ERROR" ))),
    class_mut = if_else( mut == 0, "absent", if_else( mut < median, "weak", if_else( mut >= median, "strong", "ERROR" ))),
    combination = paste0( "ant-", class_ant, "_mut-" ,class_mut)) %>%
    mutate(.,Motif = if_else( combination == "ant-absent_mut-absent","No_Interaction",
                             if_else(combination == "ant-absent_mut-strong", "Mutualist",
                             if_else(combination == "ant-absent_mut-weak", "Mutualist",
                             if_else(combination == "ant-strong_mut-absent", "Antagonist", 
                             if_else(combination == "ant-strong_mut-strong", "Mutualist-Antagonist",
                             if_else(combination == "ant-strong_mut-weak", "Antagonist-MW",
                             if_else(combination == "ant-weak_mut-absent", "Antagonist", 
                             if_else(combination == "ant-weak_mut-strong", "Mutualist-AW",
                             if_else( combination == "ant-weak_mut-weak", "Mutualist-Antagonist", "ERROR" )))))))))) %>% 
    group_by(Motif) %>%
    summarise(count = n(),
              freq  = count/n_row) %>%
    mutate(iteration = iteration) 

  return( counts )
}


```


We generated a matrix for linear discriminant analysis
```{r Matrix for LDA}
write.csv(counts, "/Users/apple/desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Interaction Motifs/Ant_Mutual_deer/im_glm_colapsed6.csv")
```


We randomized the frequency of apperance of every motif to analyzed the probability of each motif in oour interaction. Thus, we resampled 10,000 times with the frequency of each typology based on the created function
```{r Randomized frequencies}
#Define boostrap_df. We obtained the number of plants in eahc typology
boostrap_df <- compute_per_category_count (matrix_effects_resized, "real_data", median, n_row)
#Loop to generate the distribution
for (iteration in seq (1,10000) )
{
counts <- compute_per_category_count (as.data.frame(apply(matrix_effects_resized ,2,sample)), iteration, median, n_row)
boostrap_df <- rbind(counts, boostrap_df)
}

```


*We found that the values differ between the two populations. In general there is a decrease in the interaction strength between plants and animals. There is more pressure over fruits in Martinazo with a higher median valuethan in Matasgordas, perhaps beause is a smaller population where the resources are limited. Also, there are less plants with fleshy fruits.*
```{r}
write.csv(boostrap_df, "/Users/apple/desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Interaction Motifs/bs_mart_matas_mut_deer.csv")
```


Boxplot for the frequencies of interaction typologies for both populations
```{r Boxplots interaction typologies frequency}
#Martinazo
mart_im<-read.csv("boostrap_mart.csv")

boxplot(mart_im$count~mart_im$combination,data=mart_im, main="interaction motifs", 
  	xlab="Interaction motifs", ylab="frequency")

#Matasgordas
matas_im<-read.csv("boostrap_matas.csv")

boxplot(matas_im$count~matas_im$combination,data=matas_im, main="interaction motifs", 
  	xlab="Interaction motifs", ylab="frequency")

#Both Population
marti_matas_im<-read.csv("/Users/apple/desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Interaction Motifs/bs_mart_matas_mut_deer.csv")

boxplot(marti_matas_im$count~marti_matas_im$Motif,data=marti_matas_im, xlab="Interaction motifs", ylab="Frequency")
```



Reorganizing the typologies into columns to analyze the significance of each typology given the expected and observed data
```{r Motifs as columns}

#Martinazo
bs_mart<-select (mart_im, combination, count, iteration) %>% spread(.,key=combination, value=count, fill=0)

#Matasgordas
bs_matas<- select(matas_im, combination, count, iteration) %>% spread(.,key=combination, value=count, drop=TRUE)

#Both populations
marti_matas_im<-marti_matas_im[,-4] #eliminate freq column
marti_matas_im<-marti_matas_im[,-1]
bs_marti_matas<-select (marti_matas_im, Motif, count, iteration) %>% spread(.,key=Motif, value=count, fill=0)

write.csv(bs_marti_matas, "/Users/apple/desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Interaction Motifs/bs_marti_matas3.csv")

```


Creating matrix of the observed and expected data
```{r Matrixs of radom data and observed}
#"Excluding" the first row, that contain the "observed data" (row 10001)
bs_mar_mat_expected<-bs_marti_matas[-c(10001), ]

#Without column iteration
bs2<-subset(bs_mar_mat_expected[,-1])

#convert data.frame to matrix
bs3<-data.matrix(bs2)

#mean and sd for each column ("2" indicates that the selected function will be applied to each column ("1" to rows))
bs3_mean<-apply(bs3,2,mean)
bs3_sd<-apply(bs3,2,sd)


#Observed data
bs_mar_mat_observed<-bs_marti_matas[c(10001), ]
bs_obs<-subset(bs_mar_mat_observed[,-1])
bs_o<-data.matrix(bs_obs)
```

We tested the significance of appeareance of each motif in our two populations. We like two if the interactions were generated by a random a pattern or not.
```{r Z test for significance of each motif}
#Z test for each motif
alpha = .05 
z.half.alpha = qnorm(1-alpha/2) 
c(-z.half.alpha, z.half.alpha) 
#[1] -1.959964  1.959964

#No interaction
z.abs <- (bs_obs$No_Interaction - mean(bs2$No_Interaction))/sd(bs2$No_Interaction) #3.081169
# Lower 1−tailed test:
pnorm(z.abs, lower.tail=T) #p-value: 0.9999538
# Upper 1−tailed test:
pnorm(z.abs, lower.tail=F) #p−value: 4.623394e-05
#Larger than expected

#MUTUALISM_ANTAGONISM
z.mu_ant <- (bs_obs$`Mutualist-Antagonist` - mean(bs2$`Mutualist-Antagonist`))/sd(bs2$`Mutualist-Antagonist`) #-0.1563118
# Lower 1−tailed test:
pnorm(z.mu_ant, lower.tail=T) #p-value: 0.7808507
# Upper 1−tailed test:
pnorm(z.mu_ant, lower.tail=F) #p−value: 0.2191493
#Random pattern


#MUTUALIST
z.mut <- (bs_obs$Mutualist - mean(bs2$Mutualist))/sd(bs2$Mutualist) #-1.981089
# Lower 1−tailed test:
pnorm(z.mut, lower.tail=T) #p-value: 0.006255022
# Upper 1−tailed test:
pnorm(z.mut, lower.tail=F) #p−value: 0.993745
#Less than expected

#ANTAGONIST
z.ant <- (bs_obs$Antagonist - mean(bs2$Antagonist))/sd(bs2$Antagonist) #-0.6603949
# Lower 1−tailed test:
pnorm(z.ant, lower.tail=T) #p-value: 0.01413969
# Upper 1−tailed test:
pnorm(z.ant, lower.tail=F) #p−value: 0.9143158
#Less than expected

```


Bar plot of interaction motifs
```{r Bar plot for interaction motifs}
###Expected graph
#Creating long shape with the means of each motif
expect_data<-melt(bs3_mean,id.vars="Int_motif")

#naming the first column to perform the first ggplot
expect_data <- add_rownames(expect_data, "variable")

#Expected data
expect_data<-melt(bs3_mean,id.vars="Int_motif")
expect_data <- add_rownames(expect_data, "variable")
expect_data["Data"]<-NA          #adding a new column for data type
expect_data$Data<-"Random"     
expect_data["SD"]<-NA  #adding a new column for standard deviation
expect_data$SD<-bs3_sd #adding the values of standard deviation



###Observed data
obs_data<-melt(bs_o,id.vars="Int_motif")
obs_data<-melt(bs_o,id.vars="Int_motif")
obs_data<-subset(obs_data [,-1])
colnames(obs_data)<-c("variable", "value")
obs_data["Data"]<-NA        #adding a new column for data type
obs_data$Data<-"Observed" 
obs_data["SD"]<-NA     #adding a new column for standard deviation. We leave as NA because we only measure de frequency of appearence of each typology, also is helpful to the graph esthetic.


total<-rbind(obs_data,expect_data) #Joining expected and observed data


#ggplot of the observed frequencies of the motifs 
ggplot(total,aes(x=variable,y=value, fill=Data))+
       geom_bar(stat="identity",position="dodge", colour="black")+    #position an colors of the bars, (dodge refers to side by side bars)
       scale_fill_discrete(name="Data")+ xlab("Interaction Motifs")+ylab("Frequency")+ scale_y_continuous(breaks=seq(0.0,40, 2))+
       geom_errorbar(aes(ymin=value-SD, ymax=value+SD),               #addingg the sd to the bars
                width=0.2,   position=position_dodge(0.9))+
                scale_x_discrete(limits= c("No_Interaction", "Mutualist","Mutualist-Antagonist","Antagonist"))+ 
                annotate(geom="text", x=1, y=21, label="p<0.001")+annotate(geom="text", x=2, y=35, label="p=0.006")+annotate(geom="text", x=3, y=21, label="N.S.") +annotate(geom="text", x=4, y=21, label="p=0.014")+theme(legend.position = c(0.9,0.9))+theme(legend.title=element_blank())+theme(legend.text=element_text(size=rel(1.1)))+ theme(axis.title.x = element_text(size=15),axis.text.x = element_text(vjust=0.5, size=12))+theme(axis.title.y = element_text(size=15),axis.text.y = element_text(vjust=0.5, size=12))+
                theme(axis.text.x = element_text(angle = 0, hjust = 0.5))+scale_fill_manual(values = c("black", "white"))+ 
                theme(panel.background = element_blank(),axis.line = element_line(size = 0.5, linetype = "solid", colour = "black"),panel.border =                                 element_rect(colour = "black", fill=NA, size=0.5))          #formating the backgorund an lines of the graph
                



```

To analyze the relationship between the plants phenology and e performed a discriminant analysis
```{r}
im_glm <- read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Interaction Motifs/Ant_Mutual_deer/im_lda.csv")

#selecting only the explanatory variables
im_lda<-subset(im_glm[14:23])        

#Correlation matriz for explanatory variables
cor(im_lda[2:9])


#Discriminant analysis
im.lda<-lda(im_lda$motif~ inf_s+size_s+fruits_s+fruit_set_s+del.area_s+nn_s+dens_s+sincr_s, data=im_lda)
im.lda
im_p<-predict(im.lda)

im.lda1<-lda(im_lda$motif~ im_lda$inf_s+im_lda$size_s+im_lda$sincr_s+im_lda$fruits_s+im_lda$fruit_set_s+im_lda$del.area_s+im_lda$nn_s+im_lda$dens_s, data=im_lda,CV=TRUE)             #Cross validation analysis
table(im.lda1$class,im_lda[,2])                               #It seems that the worst classification i for strong and weak mutualism


#Variables useful to plot the tupologies in the coordinates LD1 and LD2
im_lda["LD1"]<-NA
im_lda$LD1<-im_p$x[,1]

im_lda["LD2"]<-NA
im_lda$LD2<-im_p$x[,2]

#Adding to the main data frame the predicted motif 
im_glm["predict_motif"]<-NA
im_glm$predict_motif<-im.lda1$class


write.csv(im_glm, "/Users/apple/desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/im_glm4.csv")

#percent correct for eahc category  
ct <- table(im_lda$motif, im.lda1$class)
diag(prop.table(ct, 1))
# total percent correct
sum(diag(prop.table(ct)))


#Plot for dicriminant analysis for motif
p<-ggplot(im_lda, aes(LD1, LD2, colour= motif))+geom_point(fill="white", size= 3, stroke=2)+
  stat_ellipse(type = "t",linetype=5)+xlim(-6,5) +theme(panel.background = element_blank(),axis.line = element_line(size = 0.5, linetype = "solid", colour = "black"),panel.border = element_rect(colour = "black", fill=NA, size=0.5))

p+labs(colour="Interaction Motifs")+theme(legend.position = c(0.12,0.88))+theme(legend.title =element_text(size=rel(1.4)))+theme(legend.text=element_text(size=rel(1.2)))+ theme(axis.title.x = element_text(size=15),axis.text.x = element_text(vjust=0.5, size=14))+theme(axis.title.y = element_text(size=15),axis.text.y = element_text(vjust=0.5, size=14))

#Plot for dicriminant analysis for population
p1<-ggplot(im_lda, aes(LD1, LD2, shape= factor(pop)))+geom_point(color="black",fill="white", size= 4, stroke=2)+
  stat_ellipse(type = "t",linetype=5)+xlim(-5,5)+theme(panel.background = element_blank(),axis.line = element_line(size = 0.5, linetype = "solid", colour = "black"),panel.border = element_rect(colour = "black", fill=NA, size=0.5))

  
p1+geom_point(aes(colour= factor(im_lda$motif)), fill="white", size= 3)+labs(shape="Population", colour="Interaction Motifs")+ theme(legend.position = c(0.12,0.8))+theme(legend.title =element_text(size=rel(1.4)))+theme(legend.text=element_text(size=rel(1.3)))+ theme(axis.title.x = element_text(size=15),axis.text.x = element_text(vjust=0.5, size=14))+theme(axis.title.y = element_text(size=15),axis.text.y = element_text(vjust=0.5, size=14))

##Plots

library(ggord)

ggord(im.lda, im_lda$motif, ellipse= TRUE, poly=FALSE)

ggord(im.lda, im_lda$pop, ellipse= TRUE, poly=FALSE)

# Wilk's lambda, stepwise selection
library(klaR)
greedy.wilks(motif~ inf_s+size_s+fruits_s+fruit_set_s+del.area_s+nn_s+dens_s+sincr_s,data = im_lda, niveau = 0.99)
#-----------------------------------------------------------------------------

# Function to plot a scatterplot matrix with a classification result
library(klaR)
classscatter(motif~ inf_s+size_s+fruits_s+fruit_set_s+del.area_s+nn_s+dens_s,data = im_lda, method = "lda")

```


```{r, by Population}

###Matasgordas
im_glm <- read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Interaction Motifs/Ant_Mutual_deer/im_lda.csv")

#selecting only Matasgordas
im_lda_Mat<-subset(im_glm[1:46,])        

#Correlation matriz for explanatory variables
cor(im_lda_Mat[2:9])


#Discriminant analysis
im.lda.Mat<-lda(im_lda_Mat$motif~ im_lda_Mat$inf_s+im_lda_Mat$size_s+im_lda_Mat$fruits_s+im_lda_Mat$fruit_set_s+im_lda_Mat$del.area_s+im_lda_Mat$nn_s+im_lda_Mat$dens_s, data=im_lda_Mat)
im.lda.Mat
im_p<-predict(im.lda.Mat)
im.lda.Mat1<-lda(im_lda_Mat$motif~ im_lda_Mat$inf_s+im_lda_Mat$size_s+im_lda_Mat$fruits_s+im_lda_Mat$fruit_set_s+im_lda_Mat$del.area_s+im_lda_Mat$nn_s+im_lda_Mat$dens_s, data=im_lda_Mat,CV=TRUE)            

#Cross validation analysis
table(im.lda.Mat1$class,im_lda_Mat[,2])                               #It seems that the worst classification i for strong and weak mutualism


#Variables useful to plot the tupologies in the coordinates LD1 and LD2
im_lda_Mat["LD1"]<-NA
im_lda_Mat$LD1<-im_p$x[,1]

im_lda_Mat["LD2"]<-NA
im_lda_Mat$LD2<-im_p$x[,2]

#Adding to the main data frame the predicted motif 
im_glm["predict_motif"]<-NA
im_glm$predict_motif<-im.lda.Mat1$class


write.csv(im_glm, "/Users/apple/desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/im_glm4.csv")

#percent correct for eahc category  
ct <- table(im_lda_Mat$motif, im.lda.Mat1$class)
diag(prop.table(ct, 1))
# total percent correct
sum(diag(prop.table(ct)))


#Plot for dicriminant analysis for motif
p<-ggplot(im_lda_Mat, aes(LD1, LD2, color= motif))+geom_point()+
  stat_ellipse(type = "t",linetype=5)+xlim(-6,9) +theme(panel.background = element_blank(),axis.line = element_line(size = 0.5, linetype = "solid", colour = "black"),panel.border = element_rect(colour = "black", fill=NA, size=0.5))


##Plots
library(devtools)
install_github("fawda123/ggord")
library(ggord)
new_lab <- list(im_lda_Mat$inf_s = 'INF', im_lda_Mat$size_s = 'SIZE', im_lda_Mat$sincr_s = 'SINCR',im_lda_Mat$fruits_s = 'FRUITS',im_lda_Mat$fruit_set_s = 'FRUIT_SET',im_lda_Mat$del.area_s = 'AREA',im_lda_Mat$nn_s = 'NN',im_lda_Mat$dens_s = 'DENS')

ggord(im.lda.Mat, im_lda_Mat$motif, ellipse= TRUE, poly=FALSE)


# Wilk's lambda, stepwise selection
library(klaR)
greedy.wilks(motif~ inf_s+size_s+fruits_s+sincr_s+fruit_set_s+del.area_s+nn_s+dens_s,data = im_lda_Mat, niveau = 0.99)

# Function to plot a scatterplot matrix with a classification result
library(klaR)
classscatter(motif~ inf_s+size_s+fruits_s+fruit_set_s+del.area_s+nn_s+dens_s,data = im_lda_Mat, method = "lda")

#_______________________________________________________________________________________
###Martinazo
#selecting only Matasgordas
im_lda_Mart<-subset(im_glm[47:70,])        

#Correlation matriz for explanatory variables
cor(im_lda_Mart[2:9])


#Discriminant analysis
im.lda.Mart<-lda(im_lda_Mart$motif~ im_lda_Mart$inf_s+im_lda_Mart$size_s+im_lda_Mart$fruits_s+im_lda_Mart$fruit_set_s+im_lda_Mart$del.area_s+im_lda_Mart$nn_s+im_lda_Mart$dens_s, data=im_lda_Mart)
im.lda.Mart
im_p<-predict(im.lda.Mart)
im.lda.Mart1<-lda(im_lda_Mart$motif~ im_lda_Mart$inf_s+im_lda_Mart$size_s+im_lda_Mart$fruits_s+im_lda_Mart$fruit_set_s+im_lda_Mart$del.area_s+im_lda_Mart$nn_s+im_lda_Mart$dens_s, data=im_lda_Mart,CV=TRUE)            

#Cross validation analysis
table(im.lda.Mart1$class,im_lda_Mart[,2])                               #It seems that the worst classification i for strong and weak mutualism


#Variables useful to plot the tupologies in the coordinates LD1 and LD2
im_lda_Mart["LD1"]<-NA
im_lda_Mart$LD1<-im_p$x[,1]

im_lda_Mart["LD2"]<-NA
im_lda_Mart$LD2<-im_p$x[,2]

#Adding to the main data frame the predicted motif 
im_glm["predict_motif"]<-NA
im_glm$predict_motif<-im.lda.Mart1$class


write.csv(im_glm, "/Users/apple/desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/im_glm4.csv")

#percent correct for eahc category  
ct <- table(im_lda_Mart$motif, im.lda.Mart1$class)
diag(prop.table(ct, 1))
# total percent correct
sum(diag(prop.table(ct)))


#Plot for dicriminant analysis for motif
p<-ggplot(im_lda_Mart, aes(LD1, LD2, color= motif))+geom_point()+
  stat_ellipse(type = "t",linetype=5)+xlim(-6,9) +theme(panel.background = element_blank(),axis.line = element_line(size = 0.5, linetype = "solid", colour = "black"),panel.border = element_rect(colour = "black", fill=NA, size=0.5))


##Plots
library(devtools)
install_github("fawda123/ggord")
library(ggord)
new_lab <- list(im_lda_Mart$inf_s = 'INF', im_lda_Mart$size_s = 'SIZE', im_lda_Mart$sincr_s = 'SINCR',im_lda_Mart$fruits_s = 'FRUITS',im_lda_Mart$fruit_set_s = 'FRUIT_SET',im_lda_Mart$del.area_s = 'AREA',im_lda_Mart$nn_s = 'NN',im_lda_Mart$dens_s = 'DENS')

ggord(im.lda.Mart, im_lda_Mart$motif, ellipse= TRUE, poly=FALSE)


# Wilk's lambda, stepwise selection
library(klaR)
greedy.wilks(motif~ inf_s+size_s+fruits_s+sincr_s+fruit_set_s+del.area_s+nn_s+dens_s,data = im_lda_Mart, niveau = 0.99)
#-----------------------------------------------------------------------------

# Function to plot a scatterplot matrix with a classification result
library(klaR)
classscatter(motif~ inf_s+size_s+fruits_s+fruit_set_s+del.area_s+nn_s+dens_s,data = im_lda_Mart, method = "lda")


```










####Changing the names of each typology, for a shorter name
levels(total$variable)[levels(total$variable)=="ant-absent_mut-absent"]<-"Abs"
levels(total$variable)[levels(total$variable)=="ant-absent_mut-strong"]<-"SM"
levels(total$variable)[levels(total$variable)=="ant-absent_mut-weak"]<-"WM"
levels(total$variable)[levels(total$variable)=="ant-strong_mut-absent"]<-"SA"
levels(total$variable)[levels(total$variable)=="ant-strong_mut-strong"]<-"SM / SA"
levels(total$variable)[levels(total$variable)=="ant-strong_mut-weak"]<-"WM / SA"
levels(total$variable)[levels(total$variable)=="ant-weak_mut-absent"]<-"WA"
levels(total$variable)[levels(total$variable)=="ant-weak_mut-strong"]<-"SM / WA"
levels(total$variable)[levels(total$variable)=="ant-weak_mut-weak"]<-"WM / WA"

#ggplot of the observed frequencies of the motifs 
ggplot(total,aes(x=variable,y=value, fill=Data))+
       geom_bar(stat="identity",position="dodge", colour="black")+    #position an colors of the bars, (dodge refers to side by side bars)
       scale_fill_discrete(name="Data")+ xlab("Motifs")+ylab("Frequency")+ scale_y_continuous(breaks=seq(0.0,18, 2))+
       geom_errorbar(aes(ymin=value-SD, ymax=value+SD),               #addingg the sd to the bars
                width=.2,   position=position_dodge(.9))+                  
                scale_x_discrete(limits= c("Abs", "SM", "WM","SM / WA", "SM / SA", "WM / WA","WM / SA","WA", "SA"))+     #giving the appropiate order of the typologies from mutualist to antagonist
                theme(axis.text.x = element_text(angle = 60, hjust = 1))+scale_fill_manual(values = c("black", "white"))+ 
                theme(panel.background = element_blank(),axis.line = element_line(size = 0.5, linetype = "solid", colour = "black"),panel.border = element_rect(colour = "black", fill=NA, size=0.5))          #formating the backgorund an lines of the graph



im_glm <- read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/im_glm.csv")

 #Creating a new column with colapsed cathegories
im_lreg <- mutate(im_glm,                    
        Motif = if_else( combination == "ant-absent_mut-absent","Absent",
                             if_else(combination == "ant-absent_mut-strong", "StrongW_Mutualism",
                             if_else(combination == "ant-absent_mut-weak", "StrongW_Mutualism",
                             if_else(combination == "ant-strong_mut-absent", "StrongW_Antagonism", 
                             if_else(combination == "ant-strong_mut-strong", "Mutualism_Antagonism",
                             if_else(combination == "ant-strong_mut-weak", "StrongW_Antagonism",
                             if_else(combination == "ant-weak_mut-absent", "StrongW_Antagonism", 
                             if_else(combination == "ant-weak_mut-strong", "StrongW_Mutualism",
                             if_else( combination == "ant-weak_mut-weak", "Mutualism_Antagonism", "ERROR" )))))))))) 
