---
title: "Interaction motifs bootstrap"
date: "July 11, 2017"
output: html_document
---

Charging libraries
```{r}
library(magrittr)
library(dplyr)
library(reshape2)
library(tidyr)
library(ggplot2)
```

Matrix
```{r}
matrix_effects_resized <- read.csv("Marti_matas.csv")
```


Settings. Minimize the effect of "weaks mutualist" we will downsize the effect of those moving the seeds less. The dispersal capacity was measured as the average weight of each mutualist, due to the seed dispersal distance is highly correlated with the body mass. The wildboars and deers where exclude because they are seed predators.
```{r}
rabbit_weight=1164
rat_weight=71
fox_weight=6000
badger_weight=6500

max_weight <- max (rabbit_weight, rat_weight, fox_weight, badger_weight)

rabbit_correction_factor = rabbit_weight / max_weight
rat_correction_factor =  rat_weight / max_weight
fox_correction_factor =   fox_weight / max_weight
badger_correction_factor = badger_weight / max_weight

```


Matrix resized by average weights, and adding NA to obtain the median of non-zero interaction values
```{r setup, include=FALSE}
matrix_effects_resized <- read.csv("Marti_matas.csv") %>%  
mutate(
    #Resize effects
    rabbit = rabbit * rabbit_correction_factor,
    rat = rat * rat_correction_factor,
    fox = fox    * fox_correction_factor,
    badger = badger * badger_correction_factor)

matrix_effects_resized_NA <- matrix_effects_resized
matrix_effects_resized_NA[matrix_effects_resized_NA==0]<-NA
median <- median(as.matrix(matrix_effects_resized_NA), na.rm=TRUE)
n_row <- nrow(matrix_effects_resized)

my_matrix<-matrix_effects_resized
```

Creating a function for the iteration results given the median. Creating a column with the triads of mutualistic and antagonistic interactions based on the interaction strength median and the frequency of the interaction motifs. The antagonistic interactions are composed by wildboar and deer; and mutualistic by rabbit, rat, badger and fox.
```{r}
compute_per_category_count <- function(my_matrix, iteration, median, n_row) {
  
  
  counts <- mutate( my_matrix,
    #Compute ant and mut effects
    ant = deer + wildboar,
    mut = (rabbit + rat ) + 
          (fox    + badger ),
    class_ant = if_else( ant == 0, "absent", if_else( ant < median, "weak", if_else( ant >= median, "strong", "ERROR" ))),
    class_mut = if_else( mut == 0, "absent", if_else( mut < median, "weak", if_else( mut >= median, "strong", "ERROR" ))),
    combination = paste0( "ant-", class_ant, "_mut-" ,class_mut)) %>%
    group_by(combination) %>%
    summarise(count = n(),
              freq  = count/n_row) %>%
    mutate(iteration = iteration)
  
  return( counts )
}
```


Creating a resample with the frequency of each typology based on the created function
```{r}
#Define boostrap_df. We obtained the number of plants in eahc typology
boostrap_df <- compute_per_category_count (matrix_effects_resized, "real_data", median, n_row)
#Loop to generate the distribution
for (iteration in seq (1,10000) )
{
counts <- compute_per_category_count (as.data.frame(apply(matrix_effects_resized ,2,sample)), iteration, median, n_row)
boostrap_df <- rbind(counts, boostrap_df)
}

```

We found that the values differ between the two populations. In general there is a decrease in the interaction strength between plants and animals. There is more pressure over fruits in Martinazo with a higher median valuethan in Matasgordas  , perhps beause is a smaller population where the resources are limited. Also, there are less plants with fleshy fruits.


```{r}
write.csv(boostrap_df, "/Users/apple/desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Interaction Motifs/boostrap_marti_matas.csv")
```


Boxplot for the frequencies of interaction typologies for both populations
```{r}
#Martinazo
mart_im<-read.csv("boostrap_mart.csv")

boxplot(mart_im$count~mart_im$combination,data=mart_im, main="interaction motifs", 
  	xlab="Interaction motifs", ylab="frequency")

#Matasgordas
matas_im<-read.csv("boostrap_matas.csv")

boxplot(matas_im$count~matas_im$combination,data=matas_im, main="interaction motifs", 
  	xlab="Interaction motifs", ylab="frequency")

#Both Population
marti_matas_im_bs<-read.csv("boostrap_marti_matas.csv")

boxplot(marti_matas_im_bs$count~marti_matas_im_bs$combination,data=marti_matas_im_bs, main="interaction motifs", 
  	xlab="Interaction motifs", ylab="frequency")
```


Reorganizing the typologies into columns to analyze the significance of each typology given the expected and observed data
```{r}

#Martinazo
bs_mart<-select (mart_im, combination, count, iteration) %>% spread(.,key=combination, value=count, fill=0)

#Matasgordas
bs_matas<- select(matas_im, combination, count, iteration) %>% spread(.,key=combination, value=count, drop=TRUE)

#Both populations
bs_marti_matas<-select (marti_matas_im_bs, combination, count, iteration) %>% spread(.,key=combination, value=count, fill=0)

write.csv(bs_marti_matas, "/Users/apple/desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Interaction Motifs/bs_marti_matas.csv")

```


Creating matrix of the observed and expected data
```{r}
#"Excluding" the first row, that contain the "observed data" (row 10001)
bs_mar_mat_expected<-bs_marti_matas[-c(10001), ]

#Without column iteration
bs2<-subset(bs_mar_mat_expected[,-1])

#convert data.frame to matrix
bs3<-data.matrix(bs2)

#mean and sd for each column ("2" indicates that the selected function will be applied to each column ("1" to rows))
bs3_mean<-apply(bs3,2,mean)
bs3_sd<-apply(bs3,2,sd)

#function to add dev. standard
error.bar <- function(x, y, upper, lower=upper, length=0.1,...){
if(length(x) != length(y) | length(y) !=length(lower) | length(lower) != length(upper))
stop("vectors must be same length")
arrows(x,y+upper, x, y-lower, angle=90, code=3, length=length, ...)
}

#Bar plot with means and with the stnd. deviation
bar_ex<-barplot(bs3_mean, ylim= c(0, 20), col = "gray", axis.lty=1, xlab="Interaction Motifs", ylab="Frequency")
error.bar(bar_ex,bs3_mean,bs3_sd)

#Observed data
bs_mar_mat_observed<-bs_marti_matas[c(10001), ]
bs_obs<-subset(bs_mar_mat_observed[,-1])
bs_o<-data.matrix(bs_obs)

bar_ob<-barplot(bs_o, ylim= c(0, 20), col = "gray", axis.lty=1, xlab="Interaction Motifs", ylab="Frequency", add = TRUE)



#Z test for each motif

alpha = .05 
z.half.alpha = qnorm(1-alpha/2) 
c(-z.half.alpha, z.half.alpha) 
#[1] -1.959964  1.959964

#ABSENT
z.abs <- (bs_obs$`ant-absent_mut-absent` - mean(bs2$`ant-absent_mut-absent`))/sd(bs2$`ant-absent_mut-absent`) #0.7486757
# Lower 1−tailed test:
pnorm(z.abs, lower.tail=T) #p-value: 0.7729737
# Upper 1−tailed test:
pnorm(z.abs, lower.tail=F) #p−value: 0.2270263
#Random pattern

#STRONG MUTUALISM
z.mstrong <- (bs_obs$`ant-absent_mut-strong` - mean(bs2$`ant-absent_mut-strong`))/sd(bs2$`ant-absent_mut-strong`) #-1.539476
# Lower 1−tailed test:
pnorm(z.mstrong, lower.tail=T) #p-value: 0.0618441
# Upper 1−tailed test:
pnorm(z.mstrong, lower.tail=F) #p−value: 0.9381559
#Marginally less frequent than expected by chance


#WEAK MUTUALISM
z.mweak <- (bs_obs$`ant-absent_mut-weak` - mean(bs2$`ant-absent_mut-weak`))/sd(bs2$`ant-absent_mut-weak`) #1.208068
# Lower 1−tailed test:
pnorm(z.mweak, lower.tail=T) #p-value: 0.8864895
# Upper 1−tailed test:
pnorm(z.mweak, lower.tail=F) #p−value: 0.1135105
#Random pattern

#STRONG ANTAGONISM
z.astrong <- (bs_obs$`ant-strong_mut-absent` - mean(bs2$`ant-strong_mut-absent`))/sd(bs2$`ant-strong_mut-absent`) #0.4453384
# Lower 1−tailed test:
pnorm(z.astrong, lower.tail=T) #p-value: 0.6719624
# Upper 1−tailed test:
pnorm(z.astrong, lower.tail=F) #p−value: 0.3280376
#Random pattern


#STRONG MUTUALISM - STRONG ANTAGONISM
z.mastrong <- (bs_obs$`ant-strong_mut-strong` - mean(bs2$`ant-strong_mut-strong`))/sd(bs2$`ant-strong_mut-strong`) #1.425802
# Lower 1−tailed test:
pnorm(z.mastrong, lower.tail=T) #p-value: 0.9230373
# Upper 1−tailed test:
pnorm(z.mastrong, lower.tail=F) #p−value: 0.07696272
#Marginally more frequent than expected

#WEAK MUTUALISM-STRONG ANTAGONISM
z.mweak_astrong <- (bs_obs$`ant-strong_mut-weak` - mean(bs2$`ant-strong_mut-weak`))/sd(bs2$`ant-strong_mut-weak`) #-2.875645
# Lower 1−tailed test:
pnorm(z.mweak_astrong, lower.tail=T) #p-value: 0.002016014
# Upper 1−tailed test:
pnorm(z.mweak_astrong, lower.tail=F) #p−value: 0.997984
##Less frequent than expected by chance


#WEAK ANTAGONISM
z.aweak <- (bs_obs$`ant-weak_mut-absent` - mean(bs2$`ant-weak_mut-absent`))/sd(bs2$`ant-weak_mut-absent`) #0.7752605
pnorm(z.aweak, lower.tail=T) #p-value: 0.7809071
# Upper 1−tailed test:
pnorm(z.aweak, lower.tail=F) #p−value: 0.2190929
#Random pattern

#STRONG MUTUALISM-WEAK ANTAGONISM
z.mstrong_aweak <- (bs_obs$`ant-weak_mut-strong` - mean(bs2$`ant-weak_mut-strong`))/sd(bs2$`ant-weak_mut-strong`) #0.8533216
# Lower 1−tailed test:
pnorm(z.mstrong_aweak, lower.tail=T) #p-value: 0.8032595
# Upper 1−tailed test:
pnorm(z.mstrong_aweak, lower.tail=F) #p−value: 0.1967405
#Random pattern

#WEAK MUTUALISM-WEAK ANTAGONISM
z.mweak_aweak <- (bs_obs$`ant-weak_mut-weak` - mean(bs2$`ant-weak_mut-weak`))/sd(bs2$`ant-weak_mut-weak`) #-0.05656088
# Lower 1−tailed test:
pnorm(z.mweak_aweak, lower.tail=T) #p-value: 0.4774475
# Upper 1−tailed test:
pnorm(z.mweak_aweak, lower.tail=F) #p−value: 0.5225525
#Random pattern



```


#Using GGplot to graph all the motifs
```{r}
###Expected graph
#Creating long shape with the means of each motif
expect_data<-melt(bs3_mean,id.vars="Int_motif")

#naming the first column to perform the first ggplot
expect_data <- add_rownames(expect_data, "variable")

#Expected data
expect_data<-melt(bs3_mean,id.vars="Int_motif")
expect_data <- add_rownames(expect_data, "variable")
expect_data["Data"]<-NA          #adding a new column for data type
expect_data$Data<-"Expected"     
expect_data["SD"]<-NA  #adding a new column for standard deviation
expect_data$SD<-bs3_sd #adding the values of standard deviation



###Observed data
obs_data<-melt(bs_o,id.vars="Int_motif")
obs_data<-melt(bs_o,id.vars="Int_motif")
obs_data<-subset(obs_data [,-1])
colnames(obs_data)<-c("variable", "value")
obs_data["Data"]<-NA        #adding a new column for data type
obs_data$Data<-"1Observed" 
obs_data["SD"]<-NA     #adding a new column for standard deviation. We leave as NA because we only measure de frequency of appearence of each typology, also is helpful to the graph esthetic.


total<-rbind(obs_data,expect_data) #Joining expected and observed data

##Changing the names of each typology, for a shorter name
levels(total$variable)[levels(total$variable)=="ant-absent_mut-absent"]<-"Abs"
levels(total$variable)[levels(total$variable)=="ant-absent_mut-strong"]<-"SM"
levels(total$variable)[levels(total$variable)=="ant-absent_mut-weak"]<-"WM"
levels(total$variable)[levels(total$variable)=="ant-strong_mut-absent"]<-"SA"
levels(total$variable)[levels(total$variable)=="ant-strong_mut-strong"]<-"SM / SA"
levels(total$variable)[levels(total$variable)=="ant-strong_mut-weak"]<-"WM / SA"
levels(total$variable)[levels(total$variable)=="ant-weak_mut-absent"]<-"WA"
levels(total$variable)[levels(total$variable)=="ant-weak_mut-strong"]<-"SM / WA"
levels(total$variable)[levels(total$variable)=="ant-weak_mut-weak"]<-"WM / WA"

#ggplot of the observed frequencies of the motifs 
ggplot(total,aes(x=variable,y=value, fill=Data))+
       geom_bar(stat="identity",position="dodge", colour="black")+    #position an colors of the bars, (dodge refers to side by side bars)
       scale_fill_discrete(name="Data")+ xlab("Motifs")+ylab("Frequency")+ scale_y_continuous(breaks=seq(0.0,18, 2))+
       geom_errorbar(aes(ymin=value-SD, ymax=value+SD),               #addingg the sd to the bars
                width=.2,   position=position_dodge(.9))+                  
                scale_x_discrete(limits= c("Abs", "SM", "WM","SM / WA", "SM / SA", "WM / WA","WM / SA","WA", "SA"))+     #giving the appropiate order of the typologies from mutualist to antagonist
                theme(axis.text.x = element_text(angle = 60, hjust = 1))+scale_fill_manual(values = c("black", "white"))+ 
                theme(panel.background = element_blank(),axis.line = element_line(size = 0.5, linetype = "solid", colour = "black"),panel.border = element_rect(colour = "black", fill=NA, size=0.5))          #formating the backgorund an lines of the graph

```

###Discriminant analysis
```{r}
im_glm <- read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Interaction Motifs/im_glm.csv")

 #Creating a new column with colapsed cathegories
im_lreg <- mutate(im_glm,                    
        Motif = if_else( combination == "ant-absent_mut-absent","Absent",
                             if_else(combination == "ant-absent_mut-strong", "StrongW_Mutualism",
                             if_else(combination == "ant-absent_mut-weak", "StrongW_Mutualism",
                             if_else(combination == "ant-strong_mut-absent", "StrongW_Antagonism", 
                             if_else(combination == "ant-strong_mut-strong", "Mutualism_Antagonism",
                             if_else(combination == "ant-strong_mut-weak", "StrongW_Antagonism",
                             if_else(combination == "ant-weak_mut-absent", "StrongW_Antagonism", 
                             if_else(combination == "ant-weak_mut-strong", "StrongW_Mutualism",
                             if_else( combination == "ant-weak_mut-weak", "Mutualism_Antagonism", "ERROR" )))))))))) 



#selecting only the explanatory variables
im_lda<-subset(im_lreg[13:25])        

#Correlation matriz for explanatory variables
cor(im_lda[1:11])

#Discriminant analysis
im.lda<-lda(im_lda$Motif~ ., data=im_lda)
im.lda
im_p<-predict(im.lda)
im.lda.p<-predict(im.lda, newdata=im_lda[,c(1:12)])$class     #predicted categories
table(im.lda.p,im_lda[,13])                                   #table with misclassifications, due the selected variables


im.lda1<-lda(im_lda$Motif~ ., data=im_lda,CV=TRUE)             #Cross validation analysis
table(im.lda1$class,im_lda[,13])                               #It seems that the worst classification i for strong and weak mutualism


#Variables useful to plot the tupologies in the coordinates LD1 and LD2
im_lda["LD1"]<-NA
im_lda$LD1<-im_p$x[,1]

im_lda["LD2"]<-NA
im_lda$LD2<-im_p$x[,2]

#Adding to the main data frame the predicted motif 
im_lreg["predict_motif"]<-NA
im_lreg$predict_motif<-im.lda1$class

#percent correct for eahc category  
ct <- table(im_lda$Motif, im.lda1$class)
diag(prop.table(ct, 1))
# total percent correct
sum(diag(prop.table(ct)))


#Plot for dicriminant analysis
p<-ggplot(im_lda, aes(LD1, LD2))
p+geom_point(aes(colour=Motif))



####Discirminant analysis without collapsed typologies
im_lda2<-subset(im_lreg[12:24])

im.lda2<-lda(im_lda2$combination~ ., data=im_lda2)
im.lda2
im_p2<-predict(im.lda2)
im.lda.p2<-predict(im.lda2, newdata=im_lda2[,c(2:13)])$class
table(im.lda.p2,im_lda2[,1])

im.lda2.1<-lda(im_lda2$combination~ ., data=im_lda2,CV=TRUE)
table(im.lda2.1$class,im_lda2[,1])

im_lda2["LD1"]<-NA
im_lda2$LD1<-im_p2$x[,1]

im_lda2["LD2"]<-NA
im_lda2$LD2<-im_p2$x[,2]



#percent correct for each category  
ct2 <- table(im_lda2$combination, im.lda2.1$class)
diag(prop.table(ct2, 1))
# total percent correct
sum(diag(prop.table(ct2)))
  
p2<-ggplot(im_lda2, aes(LD1, LD2))
p2+geom_point(aes(colour=combination))
```

