---
title: "Interaction motifs bootstrap"
author: "EMarmesat and modified by MJacome"
date: "July 11, 2017"
output: html_document
---

Charging libraries
```{r}
library(magrittr)
library(dplyr)
```

Matrix
```{r}
matrix_effects_resized <- read.csv("Marti.csv")
```


Settings. Minimize the effect of "weaks mutualist" we will downsize the effect of those moving the seeds less (distances in m). The dispersal service was measured as the distance of seed deposition by each specie. The wildboars and deers where exclude because they are seed predators.
```{r}
rabbit_dispersal_distance=1
rat_dispersal_distance=0.1
fox_dispersal_distance=2500
badger_dispersal_distance=2500

max_distance <- max (rabbit_dispersal_distance, rat_dispersal_distance, fox_dispersal_distance, badger_dispersal_distance)

rabbit_correction_factor = rabbit_dispersal_distance / max_distance
rat_correction_factor =  rat_dispersal_distance / max_distance
fox_correction_factor =   fox_dispersal_distance / max_distance
badger_correction_factor = badger_dispersal_distance / max_distance

```


Matrix resized by dispersal ditances, and adding NA to obtain the median of non-zero interaction values
```{r setup, include=FALSE}
matrix_effects_resized <- read.csv("Marti.csv") %>%  
mutate(
    #Resize effects
    rabbit = rabbit * rabbit_correction_factor,
    rat = rat * rat_correction_factor,
    fox = fox    * fox_correction_factor,
    badger = badger * badger_correction_factor)

matrix_effects_resized_NA <- matrix_effects_resized
matrix_effects_resized_NA[matrix_effects_resized_NA==0]<-NA
median <- median(as.matrix(matrix_effects_resized_NA), na.rm=TRUE)
n_row <- nrow(matrix_effects_resized)

my_matrix<-matrix_effects_resized
```

Creating a function for the iteration results given the median. Creating a column with the triads of mutualistic and antagonistic interactions based on the interaction strength median and the frequency of the interaction motifs. The antagonistic interactions are composed by wildboar and deer; and mutualistic by rabbit, rat, badger and fox.
```{r}
compute_per_category_count <- function(my_matrix, iteration, median, n_row) {
  
  
  counts <- mutate( my_matrix,
    #Compute ant and mut effects
    ant = deer + wildboar,
    mut = (rabbit + rat ) + 
          (fox    + badger ),
    class_ant = if_else( ant == 0, "absent", if_else( ant < median, "weak", if_else( ant >= median, "strong", "ERROR" ))),
    class_mut = if_else( mut == 0, "absent", if_else( mut < median, "weak", if_else( mut >= median, "strong", "ERROR" ))),
    combination = paste0( "ant-", class_ant, "_mut-" ,class_mut)) %>%
    group_by(combination) %>%
    summarise(count = n(),
              freq  = count/n_row) %>%
    mutate(iteration = iteration)
  
  return( counts )
}
```


Creating a resample with the frequency of each typology based on the created function
```{r}
#Define boostrap_df 
boostrap_df <- compute_per_category_count (matrix_effects_resized, "real_data", median, n_row)
#Loop to generate the distribution
for (iteration in seq (1,10000) )
{
counts <- compute_per_category_count (as.data.frame(apply(matrix_effects_resized ,2,sample)), iteration, median, n_row)
boostrap_df <- rbind(counts, boostrap_df)
}

```

```{r}
write.csv(boostrap_df, "/Users/apple/desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Interaction Motifs/boostrap_mart.csv")
```


Boxplot for the frequencies of interaction typologies for Martinazo
```{r}
mart_im<-read.csv("boostrap_mart.csv")
str(mart_im)


boxplot(mart_im$count~mart_im$combination,data=mart_im, main="interaction motifs", 
  	xlab="Interaction motifs", ylab="frequency")

#Without absents
mart_abs<-subset(mart_im, combination != "ant-absent_mut-absent", select=c(combination,count, freq))
boxplot(mart_abs$count~mart_abs$combination,data=mart_abs, main="interaction motifs", 
  	xlab="Interaction motifs", ylab="frequency")


```

Reorganizing the tupologies into columns Martinazo
```{r}
bs_mart<-select (mart_im, combination, count, iteration) %>% spread(.,key=combination, value=count, fill=0)
```


```{r}
matas_im<-read.csv("boostrap_matas.csv")
str(matas_im)


boxplot(matas_im$count~matas_im$combination,data=matas_im, main="interaction motifs", 
  	xlab="Interaction motifs", ylab="frequency")

#Without absents
matas_abs<-subset(matas_im, combination != "ant-absent_mut-absent", select=c(combination,count, freq))
boxplot(matas_abs$count~matas_abs$combination,data=matas_abs, main="interaction motifs", 
  	xlab="Interaction motifs", ylab="frequency")


```

Reorganizing the tupologies into columns Matasgordas
```{r}
library(tidyr)
bs_matas<-select (matas_im, combination, count, iteration) %>% spread(.,key=combination, value=count, drop=TRUE)
```

```{r}
absent<-z.test(bs_matas$`ant-absent_mut-absent`, mu= mean(bs_matas$`ant-absent_mut-absent`), sd= sd(bs_matas$`ant-absent_mut-absent`), alternative = c("two.sided"), n=length(bs_matas$`ant-absent_mut-absent`), conf.level = 0.95)

antw_mutstrong<-z.test(bs_matas$`ant-absent_mut-strong`, mu= mean(bs_matas$`ant-absent_mut-strong`), sd= sd(bs_matas$`ant-absent_mut-strong`), alternative = c("two.sided"), n=length(bs_matas$`ant-absent_mut-strong`))

antabs_mutweak<-z.test(bs_matas$`ant-absent_mut-weak`, mu= mean(bs_matas$`ant-absent_mut-weak`), sd= sd(bs_matas$`ant-absent_mut-weak`), alternative = c("two.sided"), n=length(bs_matas$`ant-absent_mut-weak`))

ants_mutabsent<-z.test(bs_matas$`ant-strong_mut-absent`, mu= mean(bs_matas$`ant-strong_mut-absent`), sd= sd(bs_matas$`ant-strong_mut-absent`), alternative = c("two.sided"), n=length(bs_matas$`ant-strong_mut-absent`))

ants_mutstrong<-z.test(bs_matas$`ant-strong_mut-strong`, mu= mean(bs_matas$`ant-strong_mut-strong`), sd= sd(bs_matas$`ant-strong_mut-strong`), alternative = c("two.sided"), n=length(bs_matas$`ant-strong_mut-strong`))

ants_mutweak<-z.test(bs_matas$`ant-strong_mut-weak`, mu= mean(bs_matas$`ant-strong_mut-weak`), sd= sd(bs_matas$`ant-strong_mut-weak`), alternative = c("two.sided"), n=length(bs_matas$`ant-strong_mut-weak`))

```

