---
title: "Efectiveness_Lndscp_Plants"
author: "Miguel Jacome"
date: "20/10/2017"
output: html_document
---

```{r setup, include=FALSE}
library(magrittr)
library(dplyr)
library(reshape2)
library(tidyr)
library(ggplot2)
library(devtools)
```


Opening a matrix file with weighted visits of frugivores in individual plants, the "row.names=1" is necessary to run the model and to detect the "name of plants" in the matrix. 
*Note: visit frequency= animal-visit-days/total-survey days.*

```{r opening visits matrix}
#Both populations
mart_matas_visits<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/mart_matas_visits_pop.csv",header=TRUE,check.names=FALSE,row.names=1)

#Without column pop
mm_visits<-subset(mart_matas_visits[,-7])

#convert data.frame to matrix
mm_visits<-data.matrix(mm_visits)

#mean and sd for each column ("2" indicates that the selected function will be applied to each column ("1" to rows))
mm_visits_mean<-apply(mm_visits,1,mean)
mm_visits_sd<-apply(mm_visits,1,sd)

#Creating long shape with the means of each motif

mm_visits_long<-melt(mm_visits_mean,id.vars="mean")
colnames(mm_visits_long) <- "visit_mean"
mm_visits_long["SE"]<-NA  #adding a new column for standard error
mm_visits_long$SE<-mm_visits_sd/sqrt(length(mm_visits_mean)) #adding the values of standard error

#naming the first column
mm_visits_long <- add_rownames(mm_visits_long, "plant")

```


Opening a matrix file with weighted links with frugivores fruit removal in individual plants. Other specifications of the matrix are described in the fruits visits file. *Note: fruit removal= animal-fruits-days/total-fruits.*

```{r}
#Both poulations
mart_matas_fruits<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/Mart_matas_fruits.csv",header=TRUE,check.names=FALSE,row.names=1)


#Without column unknown
mm_fruits<-subset(mart_matas_fruits[,-7])

#convert data.frame to matrix
mm_fruits<-data.matrix(mm_fruits)

#mean and sd for each column ("2" indicates that the selected function will be applied to each column ("1" to rows))
mm_fruits_mean<-apply(mm_fruits,1,mean)
mm_fruits_sd<-apply(mm_fruits,1,sd)

#Creating long shape with the means of each motif
mm_fruits_long<-melt(mm_fruits_mean,id.vars="mean")
colnames(mm_fruits_long) <- "fruit_mean"
mm_fruits_long["SE_f"]<-NA  #adding a new column for standard deviation
mm_fruits_long$SE_f<-mm_fruits_sd/sqrt(length(mm_fruits_mean)) #adding the values of standard deviation

#naming the first column
mm_fruits_long <- add_rownames(mm_fruits_long, "plant")

mm_fruits_long<-mm_fruits_long[,-1]
#Join coulumns
mm_total<-cbind(mm_visits_long,mm_fruits_long)

#Adding columns pop and motif
mm_total["pop"]<-NA
mm_total$pop<-mart_matas_visits$pop
mm_total["motif"]<-NA
mm_total$motif<-im_glm$motif

#Effectiveness plot per plant
p1<-effectiveness_plot(q1=mm_total$visit_mean,q2=mm_total$fruit_mean, pts.color=mm_total$motif, nlines=9,
                       myxlab= "Visit",
                       myylab="Handled fruits")

p2<-effectiveness_plot(q1=mm_total$visit_mean,q2=mm_total$fruit_mean, pts.color=mm_total$pop,nlines=9,
                       myxlab= "Visit",
                       myylab="Handled fruits")
```