---
title: "Efectiveness_Lndscp_Plants"
author: "Miguel Jacome"
date: "20/10/2017"
output: html_document
---

```{r setup, include=FALSE}
library(magrittr)
library(dplyr)
library(reshape2)
library(tidyr)
library(ggplot2)
library(devtools)
```


Opening a matrix file with weighted visits of frugivores in individual plants, the "row.names=1" is necessary to run the model and to detect the "name of plants" in the matrix. 
*Note: visit frequency= animal-visit-days/total-survey days.*

```{r opening visits matrix}
#Martinazo
mart_v<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/mart_visit.csv",header=TRUE,check.names=FALSE,row.names=1)

#Matasgordas
matas_v<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/matas_visit.csv",header=TRUE,check.names=FALSE,row.names=1)

#Both populations
mart_matas_visits<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/mart_matas_visits_pop.csv",header=TRUE,check.names=FALSE,row.names=1)

#Without column pop

mrt_visits<-subset(mart_v[,-7])

mtsg_visits<-subset(matas_v[,-7])

mm_visits<-subset(mart_matas_visits[,-7])



#convert data.frame to matrix

mrt_visits<-data.matrix(mrt_visits)

mtsg_visits<-data.matrix(mtsg_visits)

mm_visits<-data.matrix(mm_visits)


#mean and sd for each column ("2" indicates that the selected function will be applied to each column ("1" to rows))

mrt_visits_mean<-apply(mrt_visits,1,mean)
mrt_visits_sd<-apply(mrt_visits,1,sd)

mtsg_visits_mean<-apply(mtsg_visits,1,mean)
mtsg_visits_sd<-apply(mtsg_visits,1,sd)

mm_visits_mean<-apply(mm_visits,1,mean)
mm_visits_sd<-apply(mm_visits,1,sd)



#Creating long shape with the means of each motif

mrt_visits_long<-melt(mrt_visits_mean,id.vars="mean")
colnames(mrt_visits_long) <- "visit_mean"
mrt_visits_long["SE"]<-NA  #adding a new column for standard error
mrt_visits_long$SE<-mrt_visits_sd/sqrt(length(mrt_visits_mean)) #adding the values of standard error

mtsg_visits_long<-melt(mtsg_visits_mean,id.vars="mean")
colnames(mtsg_visits_long) <- "visit_mean"
mtsg_visits_long["SE"]<-NA  #adding a new column for standard error
mtsg_visits_long$SE<-mtsg_visits_sd/sqrt(length(mtsg_visits_mean)) #adding the values of standard error

mm_visits_long<-melt(mm_visits_mean,id.vars="mean")
colnames(mm_visits_long) <- "visit_mean"
mm_visits_long["SE"]<-NA  #adding a new column for standard error
mm_visits_long$SE<-mm_visits_sd/sqrt(length(mm_visits_mean)) #adding the values of standard error

#naming the first column
mrt_visits_long <- add_rownames(mrt_visits_long, "plant")
mtsg_visits_long <- add_rownames(mtsg_visits_long, "plant")
mm_visits_long <- add_rownames(mm_visits_long, "plant")

```


Opening a matrix file with weighted links with frugivores fruit removal in individual plants. Other specifications of the matrix are described in the fruits visits file. *Note: fruit removal= animal-fruits-days/total-fruits.*

```{r}
#Martinazo
mart_fruits<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/mart_fruits.csv",header=TRUE,check.names=FALSE,row.names=1)

#Matasgordas
matas_fruits<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/matas_fruits.csv",header=TRUE,check.names=FALSE,row.names=1)

#Both poulations
mart_matas_fruits<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/Mart_matas_fruits.csv",header=TRUE,check.names=FALSE,row.names=1)


#Without column unknown

mrt_fruits<-subset(mart_fruits[,-7])
mtsg_fruits<-subset(matas_fruits[,-7])
mm_fruits<-subset(mart_matas_fruits[,-7])


#convert data.frame to matrix
mrt_fruits<-data.matrix(mrt_fruits)
mtsg_fruits<-data.matrix(mtsg_fruits)
mm_fruits<-data.matrix(mm_fruits)


#mean and sd for each column ("2" indicates that the selected function will be applied to each column ("1" to rows))
mrt_fruits_mean<-apply(mrt_fruits,1,mean)
mrt_fruits_sd<-apply(mrt_fruits,1,sd)

mtsg_fruits_mean<-apply(mtsg_fruits,1,mean)
mtsg_fruits_sd<-apply(mtsg_fruits,1,sd)

mm_fruits_mean<-apply(mm_fruits,1,mean)
mm_fruits_sd<-apply(mm_fruits,1,sd)


#Creating long shape with the means of each motif

mrt_fruits_long<-melt(mrt_fruits_mean,id.vars="mean")
colnames(mrt_fruits_long) <- "fruit_mean"
mrt_fruits_long["SE_f"]<-NA  #adding a new column for standard deviation
mrt_fruits_long$SE_f<-mrt_fruits_sd/sqrt(length(mrt_fruits_mean)) #adding the values of standard deviation

mtsg_fruits_long<-melt(mtsg_fruits_mean,id.vars="mean")
colnames(mtsg_fruits_long) <- "fruit_mean"
mtsg_fruits_long["SE_f"]<-NA  #adding a new column for standard deviation
mtsg_fruits_long$SE_f<-mtsg_fruits_sd/sqrt(length(mtsg_fruits_mean)) #adding the values of standard deviation

mm_fruits_long<-melt(mm_fruits_mean,id.vars="mean")
colnames(mm_fruits_long) <- "fruit_mean"
mm_fruits_long["SE_f"]<-NA  #adding a new column for standard deviation
mm_fruits_long$SE_f<-mm_fruits_sd/sqrt(length(mm_fruits_mean)) #adding the values of standard deviation


#naming the first column
mrt_fruits_long <- add_rownames(mrt_fruits_long, "plants")
mrt_fruits_long<-mrt_fruits_long[,-1]

mtsg_fruits_long <- add_rownames(mtsg_fruits_long, "plants")
mtsg_fruits_long<-mtsg_fruits_long[,-1]

mm_fruits_long <- add_rownames(mm_fruits_long, "plants")
mm_fruits_long<-mm_fruits_long[,-1]


#Join coulumns

mrt_total<-cbind(mrt_visits_long,mrt_fruits_long)
mtsg_total<-cbind(mtsg_visits_long,mtsg_fruits_long)
mm_total<-cbind(mm_visits_long,mm_fruits_long)

#Adding columns pop and motif
mm_total["pop"]<-NA
mm_total$pop<-mart_matas_visits$pop
mm_total["motif"]<-NA
mm_total$motif<-im_glm$motif

#Effectiveness plot per plant
p1<-effectiveness_plot(q1=mm_total$visit_mean,q2=mm_total$fruit_mean,pts.shape=mm_total$pop, pts.color= mm_total$motif,nlines=9,
                       myxlab= "Visit",
                       myylab="Handled fruits")


p2<-effectiveness_plot(q1=mm_total$visit_mean,q2=mm_total$fruit_mean, pts.color=mm_total$pop,nlines=9,
                       myxlab= "Visit",
                       myylab="Handled fruits")
```