---
title: "Effectiveness plots"
author: "Miguel Jacome"
date: "3/8/2017"
output: html_document
---

```{r setup, include=FALSE}
library(magrittr)
library(dplyr)
library(reshape2)
library(tidyr)
library(ggplot2)
```


Opening a matrix file with weighted visits of frugivores in individual plants, the "row.names=1" is necessary to run the model and to detect the "name of plants" in the matrix. 
*Note: visit frequency= animal-visit-days/total-survey days.*

```{r opening visits matrix}
#Martinazo
mart<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/mart_visit.csv",header=TRUE,check.names=FALSE,row.names=1)

#Matasgordas
matas<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/matas_visit.csv",header=TRUE,check.names=FALSE,row.names=1)

#Both populations
mart_matas_visits<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/mart_matas_visits.csv",header=TRUE,check.names=FALSE,row.names=1)

#Without column unknown
mm_visits<-subset(mart_matas_visits[,-7])

#convert data.frame to matrix
mm_visits<-data.matrix(mm_visits)

#mean and sd for each column ("2" indicates that the selected function will be applied to each column ("1" to rows))
mm_visits_mean<-apply(mm_visits,2,mean)
mm_visits_sd<-apply(mm_visits,2,sd)

#Creating long shape with the means of each motif
mm_visits_long<-melt(mm_visits_mean,id.vars="mean")
colnames(mm_visits_long) <- "visit_mean"
mm_visits_long["SD"]<-NA  #adding a new column for standard deviation
mm_visits_long$SD<-mm_visits_sd #adding the values of standard deviation

#naming the first column
mm_visits_long <- add_rownames(mm_visits_long, "animal")

```


Opening a matrix file with weighted links with frugivores fruit removal in individual plants. Other specifications of the matrix are described in the fruits visits file. *Note: fruit removal= animal-fruits-days/total-fruits.*

```{r}
#Martinazo
mart_f<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/mart_fruits.csv",header=TRUE,check.names=FALSE,row.names=1)

#Matasgordas
matas_f<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/matas_fruits.csv",header=TRUE,check.names=FALSE,row.names=1)

#Both poulations
mart_matas_fruits<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/Mart_matas_fruits.csv",header=TRUE,check.names=FALSE,row.names=1)

#Without column unknown
mm_fruits<-subset(mart_matas_fruits[,-7])

#convert data.frame to matrix
mm_fruits<-data.matrix(mm_fruits)

#mean and sd for each column ("2" indicates that the selected function will be applied to each column ("1" to rows))
mm_fruits_mean<-apply(mm_fruits,2,mean)
mm_fruits_sd<-apply(mm_fruits,2,sd)

#Creating long shape with the means of each motif
mm_fruits_long<-melt(mm_fruits_mean,id.vars="mean")
colnames(mm_fruits_long) <- "fruit_mean"
mm_fruits_long["SD"]<-NA  #adding a new column for standard deviation
mm_fruits_long$SD<-mm_fruits_sd #adding the values of standard deviation

#naming the first column
mm_fruits_long <- add_rownames(mm_fruits_long, "animal")


#Join coulumns
mm_total<-cbind(mm_visits_long,mm_fruits_long[,-1])
str(mm_total)
mm_total["group"]<-NA  #adding a new column for standard deviation
mm_total$group<-"animals" #adding the values of standard deviation

as.data.frame(mm_total)
```

#Effectiveness landscape
```{r}
# Installation.
devtools::install_github("pedroj/effectiveness_pckg")
library(effect.lndscp)


effectiveness(mm_total[,2], mm_total[,4],mm_total$group, mm_total$animal,
   myxlab= "No. visits/12days", 
   myylab="Effectiveness/vis (No. fruits handled)")



###
    
    nlines <- 10
     alfa <- max(mm_total$fruit_mean)/max(mm_total$visit_mean)
     # sequence of (nlines) regular spaced x values for the isoclines
    xval <- seq(0, max(mm_total$visit_mean), 
        length.out=(nlines+1))[2:(nlines+1)] 
     isoc <- (xval*alfa) # values of the isoclines
    vis1<-seq(0, max(mm_total$visit_mean), length.out= 1000)
     pp<- as.data.frame(vis1)
    
    for(i in 1:nlines)
    {
        pp<- cbind(pp, isoc[i]/vis1)
    }    
    ##
     
     p1<- ggplot(mm_total, aes(x=visit_mean, y= fruit_mean)) + 
        geom_point(aes(colour=animal),size=3) +
        geom_text(size= 4, label= mm_total[,1], hjust= 1.3, vjust= 0) 

# Adding isolines -------------------------------------------------
    labelx<- rep(0.8*max(mm_total$visit_mean), nlines)
    labely<- as.vector(t(pp[800,1:nlines+1]))
     
    
    myxlab= "Visitiation Rate"
    myylab= "Handled Fruits"
    
    for(i in 1:nlines+1){ 
         p1= p1 + geom_line(aes(x, y), 
            data= data.frame(x= pp$vis1, y= pp[,i]), 
            col="blue", size = 0.25, alpha= 0.6) + 
            ylim(0, 1) +
            xlab(paste(myxlab)) + 
            ylab(paste(myylab))
    }
    
    
    
p1 + annotate("text", x= labelx, y= labely, label=paste("QC= ", round(isoc,2)), size=3) + ggtitle("Effectiveness landscape\nfor dwarf palm frugivorus") +theme(plot.title = element_text(hjust = 0.5)) + theme(
                    panel.background = element_blank(),axis.line = element_line(size = 0.5, linetype = "solid",
                                   colour = "black"),panel.border = element_rect(colour = "black", fill=NA, size=0.5))
        


```




