---
title: "Effectiveness plots"
author: "Miguel Jacome"
date: "3/8/2017"
output: html_document
---

```{r setup, include=FALSE}
library(magrittr)
library(dplyr)
library(reshape2)
library(tidyr)
library(ggplot2)
library(devtools)
```


Opening a matrix file with weighted visits of frugivores in individual plants, the "row.names=1" is necessary to run the model and to detect the "name of plants" in the matrix. 
*Note: visit frequency= animal-visit-days/total-survey days.*

```{r opening visits matrix}
#Martinazo
mart<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Visitation rate/mart_visit.csv",header=TRUE,check.names=FALSE,row.names=1)

#Matasgordas
matas<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Visitation rate/matas_visit.csv",header=TRUE,check.names=FALSE,row.names=1)

#Both populations
mart_matas_visits<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Visitation rate/mart_mat_visit.csv",header=TRUE,check.names=FALSE,row.names=1)

#Count the non-zero visits on a matrix
animal_visits<-colSums(mart_matas_visits != 0)
apply(animal_visits,2,sum)

#Without column unknown
mart_visits<-subset(mart[,-7])
matas_visits<-subset(matas[,-7])
mm_visits<-subset(mart_matas_visits[,-7])

#convert data.frame to matrix
mart_visits<-data.matrix(mart_visits)
matas_visits<-data.matrix(matas_visits)
mm_visits<-data.matrix(mm_visits)

#mean and sd for each column ("2" indicates that the selected function will be applied to each column ("1" to rows))
mart_visits_mean<-apply(mart_visits,2,mean)
mart_visits_sd<-apply(mart_visits,2,sd)

matas_visits_mean<-apply(matas_visits,2,mean)
matas_visits_sd<-apply(matas_visits,2,sd)

mm_visits_mean<-apply(mm_visits,2,mean)
mm_visits_sd<-apply(mm_visits,2,sd)

#Creating long shape with the means of each motif

mart_visits_long<-melt(mart_visits_mean,id.vars="mean")
colnames(mart_visits_long) <- "visit_mean"
mart_visits_long["SE"]<-NA  #adding a new column for standard deviation
mart_visits_long$SE<-mart_visits_sd/sqrt(length(mart_visits_long)) #adding the values of standard deviation

matas_visits_long<-melt(matas_visits_mean,id.vars="mean")
colnames(matas_visits_long) <- "visit_mean"
matas_visits_long["SE"]<-NA  #adding a new column for standard deviation
matas_visits_long$SE<-matas_visits_sd/sqrt(length(matas_visits_long)) #adding the values of standard deviation

mm_visits_long<-melt(mm_visits_mean,id.vars="mean")
colnames(mm_visits_long) <- "visit_mean"
mm_visits_long["SE"]<-NA  #adding a new column for standard error
mm_visits_long$SE<-mm_visits_sd/sqrt(length(mm_visits_mean)) #adding the values of standard error

sum(mm_visits_long$visit_sum == 0)

#naming the first column

mart_visits_long <- add_rownames(mart_visits_long, "animal")

matas_visits_long <- add_rownames(matas_visits_long, "animal")

mm_visits_long <- add_rownames(mm_visits_long, "animal")

```


Opening a matrix file with weighted links with frugivores fruit removal in individual plants. Other specifications of the matrix are described in the fruits visits file. *Note: fruit removal= animal-fruits-days/total-fruits.*

```{r}
#Martinazo
mart_f<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Fruit removal/mart_fruits.csv",header=TRUE,check.names=FALSE,row.names=1)

#Matasgordas
matas_f<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Fruit removal/matas_fruits.csv",header=TRUE,check.names=FALSE,row.names=1)

#Both poulations
mart_matas_fruits<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Fruit removal/mart_matas_fruits.csv",header=TRUE,check.names=FALSE,row.names=1)


#Without column unknown

mart_fruits<-subset(mart_f[,-7])

matas_fruits<-subset(matas_f[,-7])

mm_fruits<-subset(mart_matas_fruits[,-7])

#convert data.frame to matrix

mart_fruits<-data.matrix(mart_fruits)

matas_fruits<-data.matrix(matas_fruits)

mm_fruits<-data.matrix(mm_fruits)

#mean and sd for each column ("2" indicates that the selected function will be applied to each column ("1" to rows))

mart_fruits_mean<-apply(mart_fruits,2,mean)
mart_fruits_sd<-apply(mart_fruits,2,sd)

matas_fruits_mean<-apply(matas_fruits,2,mean)
matas_fruits_sd<-apply(matas_fruits,2,sd)

mm_fruits_mean<-apply(mm_fruits,2,mean)
mm_fruits_sd<-apply(mm_fruits,2,sd)

#Creating long shape with the means of each motif

mart_fruits_long<-melt(mart_fruits_mean,id.vars="mean")
colnames(mart_fruits_long) <- "fruit_mean"
mart_fruits_long["SE_f"]<-NA  #adding a new column for standard deviation
mart_fruits_long$SE_f<-mart_fruits_sd/sqrt(length(mart_fruits_long)) #adding the values of standard deviation

matas_fruits_long<-melt(matas_fruits_mean,id.vars="mean")
colnames(matas_fruits_long) <- "fruit_mean"
matas_fruits_long["SE_f"]<-NA  #adding a new column for standard deviation
matas_fruits_long$SE_f<-matas_fruits_sd/sqrt(length(matas_fruits_long)) #adding the values of standard deviation

mm_fruits_long<-melt(mm_fruits_mean,id.vars="mean")
colnames(mm_fruits_long) <- "fruit_mean"
mm_fruits_long["SE_f"]<-NA  #adding a new column for standard deviation
mm_fruits_long$SE_f<-mm_fruits_sd/sqrt(length(mm_fruits_mean)) #adding the values of standard deviation

#naming the first column

mart_fruits_long <- add_rownames(mart_fruits_long, "animal")

matas_fruits_long <- add_rownames(matas_fruits_long, "animal")

mm_fruits_long <- add_rownames(mm_fruits_long, "animal")

mm_fruits_long<-mm_fruits_long[,-1]
#Join coulumns

mart_total<-cbind(mart_visits_long,mart_fruits_long[,-1])
mart_total<-mutate(mart_total,
     i_group = if_else( animal == "deer","Seed-Predator", if_else(animal == "wildboar", "Seed-Predator", if_else(animal == "rabbit", "Deflesher", if_else(animal == "rat", "Deflesher", if_else(animal == "fox", "Seed-Disperser", if_else( animal == "badger", "Seed-Disperser", "ERROR" )))))))
as.data.frame(mart_total)

matas_total<-cbind(matas_visits_long,matas_fruits_long[,-1])
matas_total<-mutate(matas_total,
     i_group = if_else( animal == "deer","Seed-Predator", if_else(animal == "wildboar", "Seed-Predator", if_else(animal == "rabbit", "Deflesher", if_else(animal == "rat", "Deflesher", if_else(animal == "fox", "Seed-Disperser", if_else( animal == "badger", "Seed-Disperser", "ERROR" )))))))
as.data.frame(mart_total)

as.data.frame(matas_total)


mm_total<-cbind(mm_visits_long,mm_fruits_long)
mm_total<-mutate(mm_total,
     i_group = if_else( animal == "deer","Seed-Predator", if_else(animal == "wildboar", "Seed-Predator", if_else(animal == "rabbit", "Deflesher", if_else(animal == "rat", "Deflesher", if_else(animal == "fox", "Seed-Disperser", if_else( animal == "badger", "Seed-Disperser", "ERROR" )))))))

mm_total<-mutate(mm_total,
     recruit = if_else( animal == "deer","0.01206", if_else(animal == "wildboar","0" , if_else(animal == "rabbit", "0.286", if_else(animal == "rat", "0.286", if_else(animal == "fox", "0.179", if_else( animal == "badger", "0.179", "ERROR" )))))))

recruit<-as.numeric(mm_total$recruit)
mm_total<-cbind(mm_total[,-7],recruit)

as.data.frame(mm_total)
```

#Effectiveness landscape
```{r}
# Installation.
library(effect.lndscp)

###Martinazo

p1<-effectiveness_plot(q1=mart_total$visit_mean,q2=mart_total$fruit_mean, q1.error =mart_total$SE, q2.error = mart_total$SE_f, pts.color=mart_total$i_group,label=mart_total$animal, nlines=8, 
                   myxlab= "No. visits/10d", 
   myylab="Proportion of fruits handled")
p1+ ggtitle("Martinazo's dwarf palm frugivorus")


###Matasgordas
###

p2<-effectiveness_plot(q1=matas_total$visit_mean,q2=matas_total$fruit_mean, q1.error =matas_total$SE, q2.error = matas_total$SE_f, pts.color=matas_total$i_group,label=matas_total$animal, nlines=8, 
                   myxlab= "No. visits/10d", 
   myylab="Proportion of fruits handled")
p2+ ggtitle("Martasgordas's dwarf palm frugivorous")

```


```{r, Effectiveness and seedling survival}
#Martinazo
mart_e<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Frugivore Efficiency/mart_eff.csv",header=TRUE,check.names=FALSE,row.names=1)

#Matasgordas
matas_e<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Frugivore Efficiency/matas_eff.csv",header=TRUE,check.names=FALSE,row.names=1)

#Wihout unknown
mart_e<-subset(mart_e[,-7])
matas_e<-subset(matas_e[,-7])

#convert data.frame to matrix
mart_e<-data.matrix(mart_e)
matas_e<-data.matrix(matas_e)

#mean and sd for each column ("2" indicates that the selected function will be applied to each column ("1" to rows))

mart_emean<-apply(mart_e,2,mean)
mart_esd<-apply(mart_e,2,sd)

matas_e_mean<-apply(matas_e,2,mean)
matas_e_sd<-apply(matas_e,2,sd)

#Creating long shape with the means of each motif
mart_elong<-melt(mart_emean,id.vars="mean")
colnames(mart_elong) <- "Effectiveness"


matas_elong<-melt(matas_e_mean,id.vars="mean")
colnames(matas_elong) <- "Effectiveness"

#naming the first column
mart_elong <- add_rownames(mart_elong, "animal")

#naming the i_group column
mart_elong<-mutate(mart_elong,
     i_group = if_else( animal == "deer","Seed-Predator", if_else(animal == "wildb", "Seed-Predator", if_else(animal == "rabbit", "Deflesher", if_else(animal == "rat", "Deflesher", if_else(animal == "fox", "Seed-Disperser", if_else( animal == "badger", "Seed-Disperser", "ERROR" )))))))

#naming the recruit column
mart_elong<-mutate(mart_elong,
     recruit = if_else( animal == "deer","0.012", if_else(animal == "wildb","0" , if_else(animal == "rabbit", "0.286", if_else(animal == "rat", "0.286", if_else(animal == "fox", "0.179", if_else( animal == "badger", "0.179", "ERROR" )))))))

recruit<-as.numeric(mart_elong$recruit)
mart_elong<-cbind(mart_elong[,-4],recruit)

#naming the first column
matas_elong <- add_rownames(matas_elong, "animal")

#naming the i_group column
matas_elong<-mutate(matas_elong,
     i_group = if_else( animal == "deer","Seed-Predator", if_else(animal == "wildboar", "Seed-Predator", if_else(animal == "rabbit", "Deflesher", if_else(animal == "rat", "Deflesher", if_else(animal == "fox", "Seed-Disperser", if_else( animal == "badger", "Seed-Disperser", "ERROR" )))))))

#naming the recruit column
matas_elong<-mutate(matas_elong,
     recruit = if_else( animal == "deer","0.012", if_else(animal == "wildboar","0" , if_else(animal == "rabbit", "0.286", if_else(animal == "rat", "0.286", if_else(animal == "fox", "0.179", if_else( animal == "badger", "0.179", "ERROR" )))))))

recruit<-as.numeric(matas_elong$recruit)
matas_elong<-cbind(matas_elong[,-4],recruit)

mart_effect<-effectiveness_plot(q1=mart_elong$Effectiveness,q2=mart_elong$recruit, pts.color=mart_elong$i_group, pts.size = 5, label=mart_elong$animal, nlines=12,
                       myxlab= "Handled fruits/Visit",
                       myylab="Plant recruitment")+ theme(legend.position="none")+ggtitle("Martinazo")

matas_effect<-effectiveness_plot(q1=matas_elong$Effectiveness,q2=matas_elong$recruit, pts.color=matas_elong$i_group, pts.size = 5,label=matas_elong$animal, nlines=16,
                       myxlab= "Handled fruits/Visit",
                       myylab="Plant recruitment")+ theme(legend.position="none")+ggtitle("Matasgordas")
```


```{r}
###Both populations
mart_matas_e<-read.csv("~/Desktop/Palmito/Postdoc-Interaction Networks/C.-humilis-Fugivorous-Networks/Frugivore Efficiency/mart_matas_eff.csv",header=TRUE,check.names=FALSE,row.names=1)

#Wihout unknown
mm_e<-subset(mart_matas_fruits[,-7])
mm_e<-subset(mart_matas_e[,-7])

#convert data.frame to matrix
mm_e<-data.matrix(mm_e)
mm_e_long<-mutate(mm_e_long,
     i_group = if_else( animal == "deer","Seed-Predator", if_else(animal == "wildb", "Seed-Predator", if_else(animal == "rabbit", "Deflesher", if_else(animal == "rat", "Deflesher", if_else(animal == "fox", "Seed-Disperser", if_else( animal == "badger", "Seed-Disperser", "ERROR" )))))))

mm_e_long<-mutate(mm_e_long,
     recruit = if_else( animal == "deer","0.01206", if_else(animal == "wildb","0" , if_else(animal == "rabbit", "0.286", if_else(animal == "rat", "0.286", if_else(animal == "fox", "0.179", if_else( animal == "badger", "0.179", "ERROR" )))))))
     recruit = if_else( animal == "deer","0.01115", if_else(animal == "wildb","0" , if_else(animal == "rabbit", "0.286", if_else(animal == "rat", "0.286", if_else(animal == "fox", "0.179", if_else( animal == "badger", "0.179", "ERROR" )))))))

recruit<-as.numeric(mm_e_long$recruit)
mm_e_long<-cbind(mm_e_long[,-5],recruit)


p3<-effectiveness_plot(q1=mm_e_long$Effectiveness,q2=mm_e_long$recruit, pts.color=mm_e_long$i_group,label=mm_e_long$animal, nlines=8,
p3<-effectiveness_plot(q1=mm_e_long$Effectiveness,q2=mm_e_long$recruit, pts.color=mm_e_long$i_group,label=mm_e_long$animal, nlines=5,
                       myxlab= "Handled fruits/Visit",
                       myylab="Plant recruitment")
                      
```

